---
title: "Tracking fixed objects"
author: "Henrik Skov Midtiby"
output: html_notebook
---

# Data

The data this document is based on is from recordings from Måle strand 
dated 2018-07-04.
Three fixed objects are tracked over time and their calculated position 
is analysed.

Input data files:

* DJI_0003.MOV
* DJIFlightRecord_2018-07-04_[10-42-34].txt

# Getting an overview of the data.

```{r include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(cowplot))
library(lubridate)
library(sp)
suppressPackageStartupMessages(library(rgdal))
library(knitr)
```


```{r include=FALSE}
# Function implementation taken from 
# https://stackoverflow.com/a/30225804

LongLatToUTM<-function(x,y,zone){
  xy <- data.frame(ID = 1:length(x), X = x, Y = y)
  coordinates(xy) <- c("X", "Y")
  proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
  res <- spTransform(xy, CRS(paste("+proj=utm +zone=",zone," ellps=WGS84",sep='')))
  return(as.data.frame(res))
}
```


Load data, convert coordinates to UTM and shift the origin of the coordinate system
to be closer to the objects of interest.
```{r, message=FALSE, echo=FALSE}
interestpoints <- readr::read_csv('DJI_0003.interestpoints.csv') %>%
  mutate(time2 = as.numeric(as.POSIXct(time, origin = lubridate::origin)), 
         time2 = time2 - min(time2)) %>%
  mutate(utm_easting = LongLatToUTM(lon, lat, "32N")$X, 
         utm_northing =  LongLatToUTM(lon, lat, "32N")$Y, 
         drone_utm_easting = LongLatToUTM(`drone lon`, `drone lat`, "32N")$X, 
         drone_utm_northing = LongLatToUTM(`drone lon`, `drone lat`, "32N")$Y) %>%
  mutate(drone_utm_easting = drone_utm_easting - min(utm_easting), 
         drone_utm_northing = drone_utm_northing - min(utm_northing), 
         utm_easting = utm_easting - min(utm_easting), 
         utm_northing = utm_northing - min(utm_northing))
```



Counting the number of observtions of each fixed point.
```{r}
interestpoints %>%
  count(Name) %>%
  kable()
```


Get an overview of the three tracked objects.
```{r echo=FALSE}
interestpoints %>%
  ggplot() + 
  geom_point(aes(utm_easting, utm_northing, color=Name)) + 
  labs(subtitle = 'UTM Coordinates', 
       x = 'Easting', 
       y = 'Northing')
```




```{r echo=FALSE}
interestpoints %>%
  ggplot() + 
  geom_point(aes(utm_easting, utm_northing, color=time2)) + 
  scale_color_viridis_c() +
  facet_wrap(~Name) + 
  coord_equal() + 
  labs(color = "Time")
```



## A closer look on the three tracked elements

### Udspring

```{r echo=FALSE}
temp <- interestpoints %>%
  filter(Name == 'Udspring')

temp %>%
  ggplot() + 
  geom_segment(aes(x = utm_easting, y = utm_northing, 
                   xend = drone_utm_easting, 
                   yend = drone_utm_northing), 
               alpha = 0.2) + 
  geom_point(aes(utm_easting, utm_northing, color=time2)) + 
  scale_color_viridis_c() +
  coord_equal() + 
  labs(color = 'Time', 
       x = 'Easting [m]', 
       y = 'Northing [m]', 
       title = 'Tracking "udspring"', 
       subtitle = 'Position of UAV and target over time') + 
  theme(legend.justification = "bottom") -> plotA

temp %>%
  ggplot() + 
  geom_point(aes(x1, y1, color = time2)) + 
  expand_limits(x = c(0, 2211), y = c(0, 1243)) + 
  scale_color_viridis_c() +
  scale_y_reverse() + 
  coord_fixed() + 
  labs(color = '', 
       subtitle = 'Image coordinates', 
       x = '', 
       y = '') +
  theme(legend.position = 'none') -> plotB

temp %>%
  ggplot() + 
  geom_point(aes(utm_easting, utm_northing, color=time2)) + 
  scale_color_viridis_c() +
  coord_equal() + 
  labs(color = '', 
       x = '', 
       y = '', 
       title = '', 
       subtitle = '') +
  theme(legend.position = 'none') -> plotC

ggdraw() +
  draw_plot(plotA, 0, 0, 0.8, 1) +
  draw_plot(plotB, 0.5, 0.50, 0.5, 0.4) +
  draw_plot(plotC, 0.5, 0.02, 0.5, 0.5)
```



### Rock

```{r echo=FALSE}
temp <- interestpoints %>%
  filter(Name == 'Sten')

temp %>%
  ggplot() + 
  geom_segment(aes(x = utm_easting, y = utm_northing, 
                   xend = drone_utm_easting, 
                   yend = drone_utm_northing), 
               alpha = 0.2) + 
  geom_point(aes(utm_easting, utm_northing, color=time2)) + 
  scale_color_viridis_c() +
  coord_equal() + 
  labs(color = 'Time', 
       x = 'Easting [m]', 
       y = 'Northing [m]', 
       title = 'Tracking "sten"', 
       subtitle = 'Position of UAV and target over time') + 
  theme(legend.justification = "bottom") -> plotA

temp %>%
  ggplot() + 
  geom_point(aes(x1, y1, color = time2)) + 
  expand_limits(x = c(0, 2211), y = c(0, 1243)) + 
  scale_color_viridis_c() +
  scale_y_reverse() + 
  coord_fixed() + 
  labs(color = '', 
       subtitle = 'Image coordinates', 
       x = '', 
       y = '') +
  theme(legend.position = 'none') -> plotB

temp %>%
  ggplot() + 
  geom_point(aes(utm_easting, utm_northing, color=time2)) + 
  scale_color_viridis_c() +
  coord_equal() + 
  labs(color = '', 
       x = '', 
       y = '', 
       title = '', 
       subtitle = '') +
  theme(legend.position = 'none') -> plotC

ggdraw() +
  draw_plot(plotA, 0, 0, 0.8, 1) +
  draw_plot(plotB, 0.5, 0.50, 0.5, 0.4) +
  draw_plot(plotC, 0.5, 0.02, 0.5, 0.5)
```


### Sea weed cross

```{r echo=FALSE}
temp <- interestpoints %>%
  filter(Name == 'Weed cross')

temp %>%
  ggplot() + 
  geom_segment(aes(x = utm_easting, y = utm_northing, 
                   xend = drone_utm_easting, 
                   yend = drone_utm_northing), 
               alpha = 0.2) + 
  geom_point(aes(utm_easting, utm_northing, color=time2)) + 
  scale_color_viridis_c() +
  coord_equal() + 
  labs(color = 'Time', 
       x = 'Easting [m]', 
       y = 'Northing [m]', 
       title = 'Tracking "sea weed cross"', 
       subtitle = 'Position of UAV and target over time') + 
  theme(legend.justification = "bottom") -> plotA

temp %>%
  ggplot() + 
  geom_point(aes(x1, y1, color = time2)) + 
  expand_limits(x = c(0, 2211), y = c(0, 1243)) + 
  scale_color_viridis_c() +
  scale_y_reverse() + 
  coord_fixed() + 
  labs(color = '', 
       subtitle = 'Image coordinates', 
       x = '', 
       y = '') +
  theme(legend.position = 'none') -> plotB

temp %>%
  ggplot() + 
  geom_point(aes(utm_easting, utm_northing, color=time2)) + 
  scale_color_viridis_c() +
  coord_equal() + 
  labs(color = '', 
       x = '', 
       y = '', 
       title = '', 
       subtitle = '') +
  theme(legend.position = 'none') -> plotC

ggdraw() +
  draw_plot(plotA, 0, 0, 0.8, 1) +
  draw_plot(plotB, 0.5, 0.50, 0.5, 0.4) +
  draw_plot(plotC, 0.5, 0.02, 0.5, 0.5)
```








